The SMT Competition 2015--2018

### 2019-03-16 2018/report/table-winners-main.tex
Fix format.

\cc QF\_ANIA     & CVC4 {{[}Z3{]}} *& {CVC4} *        & {CVC4} *               & CVC4 {{[}Z3{]}} *           \\

@@

\cc QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink}   & {Boolector/MinkeyRink}\\

>>>>

\cc QF\_ANIA     & CVC4 {{[}Z3{]}} *     & {CVC4} *                 & {CVC4} *               & CVC4 {{[}Z3{]}} *          \\

@@

\cc QF\_BV       & {Boolector}           & {Boolector}            & {Boolector/MinkeyRink}   & {Boolector/MinkeyRink}     \\
